---
title: "Ploting"
author: "Mr_Ed"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Packages and Datasets

```{r}
library(tidyverse)
library(ggridges)
library(readxl)

setwd("~/Martin/Martin")



#Setting region color codes
region_colors<-c(
  "Ahafo" <- "#4B644B",
  "Ashanti" <- "#7D96AF",
  "Bono" <- "#EBA07E",
  "Bono East" <- "#09979B",
  "Central" <- "#EA879C",
  "Eastern"<- "#E5B9AD",
  "Greater Accra" <- "#CC9B7A",
  "North East" <- "#FDD835",
  "Northern" <- "#0070C0",
  
  "Oti" <- "#AE2B47",
  "Savannah" <- "#F94240",
  "Upper East"<- "#903000",
  "Upper West" <- "#0F3B6C",
  "Volta" <- "#59A77F",
  "Western" <- "#FDAE6B",
  "Western North" <- "#B173A0"
)

Age_at_first_sex_females_charts <- read_excel("chart/Age at first sex females charts.xlsx")

Age_at_first_sex_males_charts <- read_excel("chart/Age at first sex males charts.xlsx") |> 
  rename(District = distcode)

Breast_cancer_charts <- read_excel("chart/Breast cancer charts.xlsx") |> 
  rename(District = distcode)

Charts_Multiple_sexual_partners_females <- read_excel("chart/Charts_Multiple sexual partners females.xlsx")|> 
  rename(District = distcode)

Female_Alcohol_Charts <- read_excel("chart/Female Alcohol Charts.xlsx")

Multiple_sexual_partners_Males_charts <- read_excel("chart/Multiple sexual partners Males charts.xlsx")

New_Male_Alcohol_Charts <- read_excel("chart/New Male Alcohol Charts.xlsx")

Stool_disposal <- read_excel("chart/Stool disposal.xlsx")|> 
  rename(District = distcode)

Cervical_cancer_charts <- read_excel("chart/Cervical cancer charts.xlsx")







```

Define a list of the datasets loaded

```{r}
data_vec<- list(Age_at_first_sex_females_charts, Age_at_first_sex_males_charts, Breast_cancer_charts, 
             Charts_Multiple_sexual_partners_females, Female_Alcohol_Charts ,Multiple_sexual_partners_Males_charts, New_Male_Alcohol_Charts, 
             Stool_disposal, Cervical_cancer_charts)
```

## Data Manipulation

## Looping Over the list created

Define a function to be applied to the list objects

```{r}
data_vec_cleaned <- lapply(data_vec, function(d) {
  
    d <-d|>
      select(Region, District, Estimates = contains("Estimate")) |> 
      mutate(across(where(is.character), str_trim)) |>
      mutate(Region= ifelse(Region == "Upper east", "Upper East", Region), 
             Region= ifelse(Region == "Tamale", "Northern", Region)) |> 
  group_by(Region) |> 
  mutate(IQR = IQR(Estimates)) |> 
  ungroup() 
  })


```

##Plotting

```{r}
plots <- lapply(data_vec_cleaned, function(d) {
  
  plot <-d|>
    ggplot( aes(x = Estimates, y =reorder(Region, IQR), fill = Region, colour = Region)) +
    geom_density_ridges(scale = 1, rel_min_height = 0.01) +
    scale_x_continuous(d$Estimates, limits = c(0, max(d$Estimates)+20))+
    stat_summary(fun = mean,geom = "text", aes(label=round(after_stat(y),2)), size=3, vjust = -0.5, col="white")+
    scale_fill_manual(values = region_colors) +
    
    theme_ridges() +
    theme(legend.position = 'none', 
          axis.title = element_blank(), 
          axis.text = element_text(size = 10, face = "bold") 
          ) +
    
    
    geom_label(
      
      aes(x = max(Estimates)+10, y = Region, label = paste0("IQR: ", scales::percent( IQR/100, accuracy = 0.01, suffix = ""))), 
      hjust = 0,
      size = 5,
      color = "white",
      label.size = 0.25,
    ) +
    
    geom_jitter(aes(x = Estimates, colour = Region), size = 0.5, width = 0.3, height = 0.1) +
    scale_color_manual(values = region_colors) +
    theme(panel.grid.major.x = element_blank())
  
  
})
```


``` {r }

plots

```
```
## Saving the outputs

define the names of the plots

```{r warning=FALSE}
names(plots) <- c("Age_at_first_sex_females_charts", "Age_at_first_sex_males_charts", "Breast_cancer_charts", 
  "Charts_Multiple_sexual_partners_females", "Female_Alcohol_Charts" ,"Multiple_sexual_partners_Males_charts", "New_Male_Alcohol_Charts", 
  "Stool_disposal", "Cervical_cancer_charts")


# Save each plot with its specific name
lapply(names(plots), function(name) {
  # Retrieve the plot
  plot <- plots[[name]]
  
  # Define the filename with the plot's specific name
  file_path <- file.path("chart", paste0("plot_", name, ".jpg"))
  
  # Save the plot
  ggsave(filename = file_path, plot = plot, width = 10, height = 8)
})  

```
